%Author: Porter Smith
%Last Updated Jan 28th, 2016

\documentclass[letterpaper]{alec_mori_resume_template} 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

%% First and last name
\contactInfo{Porter}{Smith}
{
  %% Your contact information
  \href{mailto:flowbish@gmail.com}{flowbish@gmail.com} | 846-636-7507
}
{
  %% Other Links
  Github://\href{https://github.com/flowbish}{\bf flowbish}
  | http://\href{http://flowbish.me}{flowbish.me}/
}

%% Work
\header{Work Experience}
\subheader{University of Illinois at Urbana-Champaign | CS 241 Course Assistant}{January 2015 - Present}
\vspace{-1pt}
\information{Hold weekly office hours to help students debug class projects.}

\information{Facilitate weekly \textit{conceptual office hours} to help students with course material.}

\information{Help design and develop course material.}

\subheader{Applied Geotech | Quality Control Engineer Intern}{June 2015 - August 2015}
\vspace{-1pt}
\information{Rigorously tested concrete samples to ensure quality standards for clients.}

\information{Acted as quality control for public projects for various villages in Chicago suburbs.}

\subheader{Porter Lee Corporation | Junior Developer}{May 2013 - Aug 2015}
\vspace{-1pt}
\information{Developed and maintained internal support applications written in Pascal.}

\information{Migrated Oracle databases and developed database applications.}

\information{Speed tested and optimized network applications.}

%% Leadership
\header{Leadership}
\subheader{University of Illinois at Urbana-Champaign | SIGBED Co-chair}{Jan 2015 - Present}
\vspace{-1pt}
\information{Co-char for the UIUC branch of SIGBED, the special interest group for embedded systems.}

\information{Lead a team of peers on projects related to embedded devices, such as the restoration of a DDR dance pad.}

\subheader{University of Illinois at Urbana-Champaign | CS 241 Office Hour Team Leader}{Jan 2016 - Present}
\vspace{-1pt}
\information{Manage approx. 15 undergraduate and graduate office hour staff.}

\information{Prepare weekly meetings for course staff and train staff.}

%% Education
\header{Education}
\subheader{University of Illinois at Urbana-Champaign | B.S., Computer Science}{Aug 2013 - Dec 2016}
\vspace{-1pt}
\information{Technical GPA: 3.52}
\subheader{William Fremd High School}{Aug 2009 - May 2013}

\noindent\begin{minipage}[t]{.34\textwidth}
\miniheader{Relevant Coursework}
%% Not sure if relevant
%% \miniinformation{Artificial Intelligence}
%% \miniinformation{Numerical Methods}
\miniinformation{Algorithms}
\miniinformation{Computer Architecture}
\miniinformation{Data Structures}
\miniinformation{Distributed Systems}
\miniinformation{Embedded Programming}
\miniinformation{Network Systems}
\miniinformation{Programming Languages}
\miniinformation{System Programming}
\miniinformation{Wireless Networks}
\end{minipage}
\noindent\begin{minipage}[t]{.04\textwidth}
\hfill
\end{minipage}
%% Extracurriculars
\noindent\begin{minipage}[t]{.62\textwidth}
\miniheader{Extracurriculars}
\miniinformation{ACM \hfill 2013 - 2016}
\miniinformation{HackIllinois Volunteer \hfill 2015-2016}
\miniinformation{oSTEM \hfill 2014-2016}
\miniinformation{R|P Volunteer \hfill 2014-2015}
\miniinformation{SIGEmbedded Co-chair \hfill 2015-2016}
%% Skills
\miniheader {Skills and Interests}
\miniinformation{\textbf{Languages:} C, C++, Python, Java}
\miniinformation{\textbf{Tools:} Vim \& Emacs, Git, Linux Environment, Eclipse}
\miniinformation{\textbf{Interests:} Embedded Systems, Networking and Distributed Systems}
%% Honors
\miniheader{Distinctions}
\miniinformation{James Scholar \hfill 2013}
\miniinformation{Dean's List \hfill 2014}
\end{minipage}

\version{v2.0.1}

\end{document}
